An agent-based model for city networks based on interactions between firms

### 2019-10-02 slides.tex
slides_v1

 \begin{center}
 \includegraphics[width=0.7\textwidth]{figures/Figure2.png}
 \end{center}

@@

% la ou avant il faut surement expliquer que c'est pas totalement synthetique, que tu pars de X villes europeennes de plus de 50 000 habitants (pour les plus nuls comme moi)
% si c'est completement synthetiques, l'histoire des villes europeenes c'est pour avoir les ordres de grandeur de la hierarchie et du nombre de villes, mais c'est pas parametrise sur des vraies donnees - mais oui ca ca sera explique dans comment construire le systeme de ville synthetique.

% ok desolee je n'avais pas bien compris 
% javais mal explique ^-^

@@

    \centering

    \includegraphics[width=\textwidth]{figures/internationalization_countryGravityDecay200_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}

@@

    \textit{}

@@

\sframe{Grid exploration}{

    \centering

    \includegraphics[width=\textwidth]{figures/networkAvgCommunitySize_countryGravityDecay2100_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
}

@@

%\sframe{Grid exploration}{
%    \centering
%
%    \includegraphics[width=\textwidth]{figures/rhoFlowDistance_countryGravityDecay2100_gammaDestination2_facetwrapgammaOrigin_colorgammaSectors.png}
%}
% idem la c'est pas facile a lire pour quelqu'un qui ne connait pas. c'est quoi rhoFlowDistance?
% le gamma sector c'est le parametre de la variable secteurs donc s? 
% en fait quand j'y pense pourquoi il yq u gradien du gamma et comment comprendre ces varations pour chqaue pqs de temps

@@

\sframe{On the role of model exploration}{

@@

@@

@@

@@

$\rightarrow$ A simulation model to understand processes of network emergence

$\rightarrow$

@@

\textbf{Simulation data at}

\texttt{https://doi.org/10.7910/DVN/UPX23S}

@@

\sframe{Reserve slides}{

\centering

\Large

\textbf{Reserve Slides}

>>>>

 \begin{center}
 \includegraphics[width=0.7\textwidth]{figures/Figure2.jpg}
 \end{center}

@@

@@

    \begin{center}
    \includegraphics[width=\textwidth]{figures/internationalization_countryGravityDecay200_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
    \end{center}

@@

    \textit{The transition as a function of interaction range depends on the influence of origin size $\gamma_F$; sector proximity $\gamma_S$ plays a role only for a large influence of the origin.}

@@

\sframe{Grid exploration: community size}{

    \begin{center}
    	\includegraphics[height=0.6\textheight]{figures/networkAvgCommunitySize_countryGravityDecay2100_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
    \end{center}

    \vspace{-0.5cm}

\begin{itemize}
	\item Maximal integration in term of community size is achieved at an intermediate value of $d_G$: emergence of a regional regime
	\item Maximal size depends on the role of sectors $\gamma_S$, in a decreasing way when origin size is deactivated, and increasing way when $\gamma_F=1$
	\item This regime disappear when origin size influence is too large
\end{itemize}

@@

%\sframe{Grid exploration}{
%    \centering
%
%    \includegraphics[width=\textwidth]{figures/rhoFlowDistance_countryGravityDecay2100_gammaDestination2_facetwrapgammaOrigin_colorgammaSectors.png}
%}

% idem la c'est pas facile a lire pour quelqu'un qui ne connait pas. c'est quoi rhoFlowDistance?
% le gamma sector c'est le parametre de la variable secteurs donc s? 
% en fait quand j'y pense pourquoi il yq u gradien du gamma et comment comprendre ces varations pour chqaue pqs de temps

@@

@@

\justify
\footnotesize

@@

$\rightarrow$ effect of exogenous shocks in the socio-economic structure (``subsystem-xit'')

@@

$\rightarrow$ evolution of city sizes (co-evolution model)

$\rightarrow$ parametrization/calibration on real data

$\rightarrow$ role of path-dependency

$\rightarrow$ towards a model with firm agents? (multi-scale ABM)

\textbf{On the role of model exploration}

$\rightarrow$ even with such a ``simple'' model (close to directly tractable stationary state), behavior is highly non-linear in many dimensions

$\rightarrow$ model exploration allows to overcome hidden parameters (deactivated mechanisms or default parameter values)

$\rightarrow$ exploration of intrinsic dynamics on synthetic data is a crucial step before an application on real data (disentangle effects of geography from model dynamics)

@@

$\rightarrow$ A generative model to understand processes of economic network emergence

$\rightarrow$ Crucial role of model exploration to validate and extract knowledge from such a simulation model

@@

\textbf{Simulation data at} \texttt{https://doi.org/10.7910/DVN/UPX23S}

@@
